Supplementary Material for Asymmetry paper

### 2020-05-11 Supplementary/Sup_mat.Rmd
minor edits.

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package. We then investigated how well we could detect various effects, and how this varied based on the sample size. See Figure 1a.

>>>>

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package, as illustrated in Figure 1a. The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\sim0$.

We then investigated how well we could detect various effects (i.e., increases in the mean from $\mu=0$ to $\mu=0.01$), and how this varied based on the sample size.
